---
title: "Assignment_1_34334912"
author: "Aatish Prasad"
format: html
---

```{r}
#| include: false
#| message: false
#| warning: false
library(tidyverse)
library(knitr)
library(kableExtra)
```

Test

```{r}
data <- read_csv("data/34334912_Aatish Prasad.csv")
```

# INTRODUCTION

This data set analysis aims to investigate the relationship between customer purchasing behaviour and targeted marketing expenditure. It seeks to determine whether increased marketing spending can have a significant influence on consumer behaviour. We also account for a variety of influential factors, such as how often the customer is transacting, how long the customer has been transacting, as well as the type of customer. This provides a more rounded, multivariate basis for our analysis. Understanding the the relationship between these factors and the importance of their interconnectivity is an important step in optimising business decisions.

### **Research Question section (2 points)**

In this report we investigate whether an increase in marketing expenditure would have a significant increase in customer purchasing expenditure. It also accounts for other factors that might have an effect on purchase decisions. The purpose of this report is to identify the key drivers of purchasing behaviour and make a comparative analysis of marketing expenditure against other factors on this behaviour.

# Data Set Introduction

```{r}
data_clean <- data %>% 
  distinct() %>% 
  mutate(
  # Convert missing values to NA
    across(c(signup_date, segment, notes), ~na_if(., "N/A")), 
      
  # Convert date to standard format
  signup_date = coalesce(
  dmy(signup_date),
  mdy(signup_date))
  
    )
  
```

The data set contains customer purchasing behaviour in relation to marketing expenditure and other variables. These include customer id, which uniquely identifies the customers, the customer segment(whether they are individuals, small businesses or enterprises) and notes about the interaction between the customer and the organisation recording these observations, all of which are stored as strings. There is also marketing spend (amount spent on marketing to a customer), the number of visits, and the total amount the customer has spent on purchases, which are recorded as double attributes. Finally, we include a signup_date, which is a Day attribute recording the date when the customer first made a transaction.

To clean the data set, we ran the distinct function to remove duplicates, converted the "N/A" records into R-readable "NA" and converted the date column into a standard format for further operations.

## Dataset Description

```{r}
nrow(data_clean)
ncol(data_clean)
glimpse(data_clean)
```

The dataset **data_clean** contains `r nrow(data_clean)` observations and `r ncol(data_clean)` variables.

```{r}
#| label: fig-boxplot
#| fig-cap: "Distribution of purchase amount by customer segment"

data_clean %>% 
  ggplot(aes(x = segment, y = purchase_amount)) +
  geom_boxplot(na.rm = TRUE) +
  labs(
    x = "Customer Segment",
    y = "Purchase Amount"
  )

```

@fig-boxplot shows the median and interquartile range of purchase amount for each customer segment. As we can see, Small and Medium Businesses (SMB) exhibit the highest median purchase amount of the three, indicating that they tend to spend more on average.

```{r}
#| label: tbl-summary
data_clean %>%
  group_by(segment) %>% 
  summarise(
    count = n(),
    avg_purchase = mean(purchase_amount, na.rm = TRUE),
    median_purchase = median(purchase_amount, na.rm = TRUE),
    avg_marketing = mean(marketing_spend, na.rm = TRUE),
    avg_visits = mean(visits, na.rm =TRUE)
  ) %>% 
  kable(caption = "Summary Statistics") %>% 
   kable_styling(
    full_width = FALSE,
    position = "center",
    bootstrap_options = c("bordered")
  )
```

@tbl-summary shows summary statistics of the purchasing amount of each customer segment. This supports @fig-boxplot in the claim that SMBs have higher purchasing spend, over less number of visits
